\paragraph{Compatibility entries.}
The entries \(\texttt{GraphParam}\), \(\texttt{twinWidth}\), and
\(\texttt{treewidth}\) are retained for compatibility with the already-imported
surface of this submission.  They are aliases for the graph-parameter type
\[
  \forall V,\; [\mathrm{Fintype}\ V] \to [\mathrm{DecidableEq}\ V] \to
    \mathrm{SimpleGraph}\ V \to \mathbb{N},
\]
the concrete twin-width parameter from the vendored source, and the concrete
treewidth parameter from the vendored source.

The compatibility theorem states that for every natural number \(k\), there is
a finite type \(V\), decidable equality on \(V\), and a simple graph \(G\) on
\(V\) such that
\[
  \operatorname{tw}(G) \le 2k+4
  \qquad\text{and}\qquad
  2^k < \operatorname{tww}(G).
\]

\paragraph{Expanded statement.}
The new expanded theorem states the same Bonnet--Depres separation but spells
out both graph parameters in the Lean statement itself.  It expands treewidth
directly as the natural-number minimum, implemented by \(\texttt{Nat.find}\),
of all widths \(w\) for which \(G\) has a finite tree decomposition whose
largest bag has size at most \(w+1\).  Equivalently, a witness is a tree
decomposition \(D\) with
\[
  \Bigl(\max_i |D_i|\Bigr)-1 \le w .
\]

The Lean statement also expands twin-width directly as the natural-number
minimum, again implemented by \(\texttt{Nat.find}\), of all red-degree bounds \(d\) for
which \(G\) has a contraction sequence of width at most \(d\).  Thus the
second inequality says that every contraction sequence of the graph has width
strictly greater than \(2^k\).

\paragraph{Proof content.}
The proof instantiates \(G\) with the explicit Bonnet--Depres graph
\(BD_k\).  The submitted proof then uses the proved tree-decomposition bound
\(\operatorname{tw}(BD_k) \le 2k+4\) and the proved lower bound
\(\operatorname{tww}(BD_k) > 2^k\).  Both the compatibility theorem and the
expanded theorem are proved directly from these source lemmas.  No contract
axiom supplies either result: the lower bound is proved from the
Bonnet--Depres construction in the vendored source files.
